Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-04 Paper/results.tex
Added Myra edits

To determine the appropriate mesh size and resolution, a grid study
was conducted using the stable 5m/s ABL case and the Nalu-Wind code.
A number of cases were set up using the surface roughness and
prescribed temperature decreases listed in table
\ref{tab:z0tempparam}, but with varying grid resolutions and
conservative estimates for the domain size required.  As shown in
table \ref{tab:GridStudySetup}, the horizontal resolutions varied from
10m to 2.5m cells for the coarse and fine cases, respectively.  All
simulations for the grid study also used a vertical resolution of
dz=2.5m and the same vertical extent of 1km.

%%%%%%%%%%%%%%% GRID STUDY: INTEGRAL LENGTH %%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\caption{\label{tab:GridStudySetup} The setup for the grid resolution study} \centering
\begin{tabular}{ccccc}
  \hline
  Case              & dx [m] & dy [m] & dz [m] & Domain size \\
  \hline
  Nalu-Wind coarse  &  10.0  & 10.0   & 2.5 & 1.5km $\times$ 1.5km $\times$ 1.0km  \\
  Nalu-Wind medium  &   5.0  &  5.0   & 2.5 & 1.5km $\times$ 1.5km $\times$ 1.0km  \\
  Nalu-Wind fine    &   2.5  &  2.5   & 2.5 & 1.0km $\times$ 1.0km $\times$ 1.0km  \\
% AMR-wind fine     &   2.5  &  2.5   & 2.5 & 0.0 \\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The comparison of the wind spectra and maximum resolvable frequency
$f_{max}$ for the different mesh resolutions is shown in figure
\ref{fig:GridStudySpectra}.  Here spectra is shown at the $z$=20m
height and averaged using 1/3 octave-bins to enhance clarity. For the
$S_u$ and $S_w$ spectra, there are noticeable shifts in the peak
amplitude, while the peak amplitudes for $S_v$ remained fairly
constant between cases.  In all cases, the peak frequency of $S_i(f)$
also increased as the resolution increased. While the mesh resolution
was sufficient to capture the peak frequency for $S_u$, the fine
resolution with 2.5m mesh cells was required to capture the spectral
peaks in the lateral and vertical directions.

The second metric for determining the appropriate grid size and mesh
resolution is through the correlation tensor and turbulence integral
length scale.  The two-point correlation tensor
$R_{ij}(\mathbf{x},\boldsymbol{\xi})$ at position $\mathbf{x}$ and
separation vector $\boldsymbol{\xi}$ is defined as
\begin{equation}
  \label{eq:Rij}
  R_{ij}({\mathbf x},\boldsymbol{\xi}) =
  \frac{\overline{ {u'_i(\mathbf{x}, t) u'_j(\mathbf{x}+\boldsymbol{\xi},t)} }}
       { \sqrt{\overline{ u'^2_i }} \sqrt{\overline{ u'^2_j}} }
\end{equation}
where the velocity fluctuations $u'_i$ are defined as
\begin{equation}
  u'_i(\mathbf{x},t) = u_i(\mathbf{x},t) - \overline{ u_i(\mathbf{x},t) }
\end{equation}
and the overbar operator $\overline{(\bullet)}$ denotes time
averaging.  In the current study, we compute the horizontally averaged
correlation coefficient $\langle R_{11}(\boldsymbol{\xi})\rangle$ by
sampling over multiple points at the $z$=20m height, typically 100-150
points, and averaging the result.  The longitudinal $\langle
R_{11}(\boldsymbol{\xi})\rangle$ was calculated by looking at
separation vectors $\boldsymbol{\xi}$ in the streamwise direction
while the lateral $\langle R_{11}(\boldsymbol{\xi})\rangle$ used
separation distances $\boldsymbol{\xi}$ which were orthogonal to the
wind direction on the same horizontal plane.

%%%%%%%%%%% Grid resolution Rij correlation figure %%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/GridStudy/GridStudy_Rij.ipynb
\begin{figure}%[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/GridStudy_Rij_Longitudinal.png}
  \includegraphics[width=2.5in]{figures/GridStudy_Rij_Lateral.png}
  \caption{\label{fig:GridStudyRij} Calculation of the averaged
    longitudinal and lateral $\langle R_{11}(\boldsymbol{\xi})
    \rangle$ coefficients at $z$=20m for LES of stable 5m/s case with
    different resolutions.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Based on this longitudinal length scale, we also determined the
overall domain size necessary for stable ABL calculations.  To provide
sufficient space to ensure development and decorrelation of turbulent
structures, domain sizes of approximately 10 times the longitudinal
lengthscale is recommended.  However, the inclusion of sample probes
with sufficient separation distance to accurately calculate $\langle
R_{11}(\boldsymbol{\xi}) \rangle$ roughly doubles the domain size
requirements.  Assuming the longitudinal length scales on the order of
30 m, we estimated a minimum domain size of 750m $\times$ 750m in the
horizontal directions for both the Nalu-Wind and AMR-Wind LES
calculations.

@@

After running each case for 15,000 seconds, the boundary layer
statistics and horizontally averaged profiles were averaged for
another 5,000 seconds.  In table \ref{tab:CompareAMRvsNalu}, some mean
statistics are given for both cases, including the friction velocity
$u_\tau$, the turbulence intensity TI at z=20m, and local shear
exponent $\alpha$ at z=20m, defined as
$$ \alpha = \frac{z}{U_{horiz}} \frac{d U_{horiz}}{dz}.
$$ AMR-Wind and Nalu-Wind produced nearly identical values for the
TI=0.048, which is close to measured target of 4.5\%, and similar
agreement was found for the shear exponent $\alpha$.  A minor
descrepancy was found in the friction velocity $u_\tau$, with AMR-Wind
resulting in a value slightly lower than Nalu-Wind.

The comparison of the horizontally averaged wind profiles is shown in
figure \ref{fig:CompareAMRvsNaluWind_WSDir}.  At the forcing height
z=20m, the wind speed and wind shear are close to an exact match
between the two LES codes.  The horizontal wind speeds continue to
agree well for $z$<100m, beyond which a relatively constant velocity
difference is observed.   For both AMR-Wind and Nalu-Wind, an
approximately linear veer profile was observed until $z\approx$ 250m,
at which point the wind direction remained constant until the
inversion layer height.

@@

%%%%%%%%%%% Compare Nalu/AMR WS/WDir profiles %%%%%%%%%%%%%%%%%%%%%%%
% Postprocessing/ABLStats/AMRWind_NaluWind_stable_05ms_mesh2_5x2_5x2_5_paper.ipynb
\begin{figure} %[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_WS.png}
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_Wdir.png}\\
  \caption{\label{fig:CompareAMRvsNaluWind_WSDir} Comparison of
    AMR-Wind and Nalu-Wind horizontal velocity and wind direction
    profiles for the stable 5 m/s boundary layer. The dashed
    horizontal line corresponds to the measurement height z=20m. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% Compare Nalu/AMR TI/Temp profiles %%%%%%%%%%%%%%%%%%%%%%
% Postprocessing/ABLStats/AMRWind_NaluWind_stable_05ms_mesh2_5x2_5x2_5_paper.ipynb
\begin{figure} [hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_TI.png}
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_T.png}
  \caption{\label{fig:CompareAMRvsNaluWind_TTI} Comparison of AMR-Wind
    and Nalu-Wind turbulence intensity and temperature profiles for
    the stable 5 m/s boundary layer. The dashed horizontal line
    corresponds to the measurement height z=20m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

  \caption{\label{fig:CompareAMRvsNaluSpectra} Comparison of AMR-Wind
    and Nalu-Wind wind spectra at z=20m for the stable 5 m/s boundary
    layer. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%   \caption{\label{fig:CompareAMRvsNaluRij}
%%     Comparison of AMR-Wind and Nalu-Wind $\langle R_{11}
%%     \rangle$ correlation at z=20m. }
%% \end{figure}
%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Using the results of the stable cases described in \ref{sec:CFDsetup},
as well as the computations from the previous study in
\cite{cheung2020large}, we can examine the influence of wind speed and
stratification on offshore ABL behavior.  In this section we first
compare the differences between the three stable ABL cases, and then
compare their behavior with the previously computed neutral and
unstable counterparts.

\subsubsection{\label{sec:stableABLStats} ABL integrated quantities}
From the AMR-Wind calculations of the stable ABL at 5m/s, 10m/s, and
15m/s, a number of quantities can be computed to compare with the
measured targets from Archer et al \cite{archer2016predominance}.  In
table \ref{tab:CompareAMRallWS}, we list the TI, shear exponent
$\alpha$, friction velocity $u_\tau$, Obukhov length $L_{Ob}$,
longitudinal lengthscale $L$, and stability classification for each of
these three cases.  The TI values, calculated at the height $z$=20m
fall within the target range of 4.5\% to 6.0\% for stable conditions
from the Cape Wind measurements.  The calculated friction velocities
are also similar to the values from the neutral offshore ABL
calculations of \cite{cheung2020large}, where $u_\tau$ varied from
0.15 m/s to 0.51 m/s for wind speeds of 5 m/s to 15 m/s.

@@

%%%%%%%%%%%%%%% Compare AMR integrated quantities, all WS %%%%%%%%%%%%%%
% See Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{table}
\caption{\label{tab:CompareAMRallWS} Comparison of Stable ABL for all
  wind speeds} \centering
\begin{tabular}{cccccccc}
  \hline
  Code & Wind speed   & TI     & $\alpha$& $u_\tau$ & Obukhov $L_{Ob}$ & Longitudinal $L$ & Stability \\
  \hline
  AMRWind & 5m/s      & 0.0483 &  0.166 &  0.157 m/s  &  52.5 m & 27.7 m  & Very stable\\
  AMRWind & 10m/s     & 0.0506 &  0.160 &  0.319 m/s  &  57.2 m & 29.6 m  & Very stable\\
  AMRWind & 15m/s     & 0.0550 &  0.118 &  0.511 m/s  & 131.3 m & 43.8 m  & Stable \\
  \hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The qualitative behavior of the stable boundary layers can be seen
through snapshots of the flow taken from each of the simulations.  In
figure \ref{fig:SnapshotsZ20}, instantaneous snapshots of the
horizontal and vertical velocities for each of the three cases at the
z=20m measurement height are shown.  The largest difference can be
seen in the size of the flow structures between the very unstable and
stable cases.  Longer streaks are evident in the 15 m/s case compared
to the 5 m/s and 15 m/s cases, which is consistent with the nearly
50\% larger integral lengthscale $L$ given in table
\ref{tab:CompareAMRallWS}.  The differences in the vertical velocity
are also evident in figure \ref{fig:SnapshotsZ20}.  At higher wind speeds the
magnitude of the vertical $w'$ fluctuations increase, which plays a
strong role in the growth of the boundary layer.

%%%%%%%%%%% z=20m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \begin{tikzpicture}
    % 5 m/s plots
    \node[anchor=south west, inner sep=0](image) at (0in,4.50in)
         {\includegraphics[width=3in]{figures/snapshots/05ms/velh_mag_z20.png}};
    \node[align=left] at (1in, 4.50in){(a) horizontal vel, 5 m/s};
    \node[anchor=south west, inner sep=0](image) at (3in,4.35in)
         {\includegraphics[width=3.20in]{figures/snapshots/05ms/velz_z20_samelimits.png}};
    \node[align=left] at (4.25in, 4.50in){(b) vertical vel, 5 m/s};

@@

  \end{tikzpicture}
  \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal
    velocity and vertical velocity, taken at t=20,000 seconds of the
    simulations at height z=20m, for the AMR-Wind calculation of the
    stable 5 m/s, 10 m/s, and 15 m/s ABL. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Horizontally averaged flow profiles shown in figures
\ref{fig:CompareAMRallWS} and \ref{fig:CompareAMRallTTI} provide a
more quantitative assessment of the ABL evolution.  The rapid growth
of the 15 m/s stable case leads to strong shear throughout the
boundary layer up to the inversion height, while the very stable 5 m/s
and 10 m/s cases showed minimal shear at higher elevations (figure \ref{CompareAMRallWS}).  The
change in wind direction is also indicative of the boundary layer
penetration.  Approximately linear veer profiles are visible up to
heights of $z\approx$250 m and $z\approx$350 m for the 5 m/s and 10
m/s cases, respectively, while the linear veer is present in the 15
m/s stable case up to $z$=650m.

The behavior of the TI and temperature profiles in figure
\ref{fig:CompareAMRallTTI} closely follows the shear and veer profiles
discussed above.  Despite all cases reaching a similar TI levels at
$z$=20m, the turbulence decays at different rates for each case until
reaching the top of the boundary layer.  The effect of the different
surface temperature changes is also visible in the horizontally
averaged temperature profiles.  Both the 10 m/s and 15 m/s impose
similar temperature changes (-1.4 K/hr and -1.5 K/hr, respectively)
and similar temperatures at the ocean surface.  However, the
cooling effect in the very stable 10 m/s case is limited to $z$<350
m, similar to the veer and turbulence profiles.

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WS.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WDir.png}
  \caption{ \label{fig:CompareAMRallWS} Comparison of the horizontal
    wind speed and wind direction profile for the stable 5m/s, 10m/s,
    and 15m/s boundary layers. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_TI.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_T.png}
  \caption{ \label{fig:CompareAMRallTTI} Comparison of the turbulence
    intensity and temperature profile for the stable 5m/s, 10m/s, and
    15m/s boundary layers. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

To determine the appropriate mesh size and resolution, a grid study
was conducted using the stable 5m/s ABL case and the Nalu-Wind code.
A number of cases were set up using the surface roughness and
prescribed temperature decreases listed in table
\ref{tab:z0tempparam}, but with varying grid resolutions and
conservative estimates for the domain size required.  As shown in
table \ref{tab:GridStudySetup}, the horizontal resolutions varied from
10 m to 2.5 m cells for the coarse and fine cases, respectively.  All
simulations for the grid study also used a vertical resolution of
dz=2.5 m and the same vertical extent of 1 km.

%%%%%%%%%%%%%%% GRID STUDY: INTEGRAL LENGTH %%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\caption{\label{tab:GridStudySetup} The setup for the grid resolution study} \centering
\begin{tabular}{ccccc}
  \hline
  Case              & dx [m] & dy [m] & dz [m] & Domain size \\
  \hline
  Nalu-Wind coarse  &  10.0  & 10.0   & 2.5 & 1.5 km $\times$ 1.5km $\times$ 1.0 km  \\
  Nalu-Wind medium  &   5.0  &  5.0   & 2.5 & 1.5 km $\times$ 1.5 km $\times$ 1.0 km  \\
  Nalu-Wind fine    &   2.5  &  2.5   & 2.5 & 1.0 km $\times$ 1.0 km $\times$ 1.0 km  \\
% AMR-wind fine     &   2.5  &  2.5   & 2.5 & 0.0 \\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The comparison of the wind spectra and maximum resolvable frequency
$f_{max}$ for the different mesh resolutions is shown in figure
\ref{fig:GridStudySpectra}.  Here spectra is shown at the $z$=20 m
height and averaged using 1/3 octave-bins to enhance clarity. For the
$S_u$ and $S_w$ spectra, there are noticeable shifts in the peak
amplitude, while the peak amplitudes for $S_v$ remained fairly
constant between cases.  In all cases, the peak frequency of $S_i(f)$
also increased as the resolution increased. While the mesh resolution
was sufficient to capture the peak frequency for $S_u$, the fine
resolution with 2.5m mesh cells was required to capture the spectral
peaks in the lateral and vertical directions.
\fxnote{OK for temporal resolution}

The second metric for determining the appropriate grid size and mesh
resolution is through the correlation tensor and turbulence integral
length scale.  The two-point correlation tensor
$R_{ij}(\mathbf{x},\boldsymbol{\xi})$ at position $\mathbf{x}$ and
separation vector $\boldsymbol{\xi}$ is defined as
\begin{equation}
  \label{eq:Rij}
  R_{ij}({\mathbf x},\boldsymbol{\xi}) =
  \frac{\overline{ {u'_i(\mathbf{x}, t) u'_j(\mathbf{x}+\boldsymbol{\xi},t)} }}
       { \sqrt{\overline{ u'^2_i }} \sqrt{\overline{ u'^2_j}} }
\end{equation}
where the velocity fluctuations $u'_i$ are defined as
\begin{equation}
  u'_i(\mathbf{x},t) = u_i(\mathbf{x},t) - \overline{ u_i(\mathbf{x},t) }
\end{equation}
and the overbar operator $\overline{(\bullet)}$ denotes time
averaging.  In the current study, we compute the horizontally averaged
correlation coefficient $\langle R_{11}(\boldsymbol{\xi})\rangle$ by
sampling over multiple points at the $z$=20 m height, typically 100-150
points, and averaging the result.  The longitudinal $\langle
R_{11}(\boldsymbol{\xi})\rangle$ was calculated by looking at
separation vectors $\boldsymbol{\xi}$ in the streamwise direction
while the lateral $\langle R_{11}(\boldsymbol{\xi})\rangle$ used
separation distances $\boldsymbol{\xi}$ which were orthogonal to the
wind direction on the same horizontal plane.

%%%%%%%%%%% Grid resolution Rij correlation figure %%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/GridStudy/GridStudy_Rij.ipynb
\begin{figure}%[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/GridStudy_Rij_Longitudinal.png}
  \includegraphics[width=2.5in]{figures/GridStudy_Rij_Lateral.png}
  \caption{\label{fig:GridStudyRij} Calculation of the averaged
    longitudinal and lateral $\langle R_{11}(\boldsymbol{\xi})
    \rangle$ coefficients at $z$=20 m for LES of stable 5m/s case with
    different resolutions.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Based on this longitudinal length scale, we also determined the
overall domain size necessary for stable ABL calculations.  To provide
sufficient space to ensure development and decorrelation of turbulent
structures, domain sizes of approximately 10 times the longitudinal
lengthscale is recommended.  However, the inclusion of sample probes
with sufficient separation distance to accurately calculate $\langle
R_{11}(\boldsymbol{\xi}) \rangle$ roughly doubles the domain size
requirements.  Assuming the longitudinal length scales on the order of
30 m, we estimated a minimum domain size of 750 m $\times$ 750 m in the
horizontal directions for both the Nalu-Wind and AMR-Wind LES
calculations.

@@

After running each case for 15,000 seconds, the boundary layer
statistics and horizontally averaged profiles were averaged for
another 5,000 seconds.  In table \ref{tab:CompareAMRvsNalu}, some mean
statistics are given for both cases, including the friction velocity
$u_\tau$, the turbulence intensity TI at z=20 m, and local shear
exponent $\alpha$ at z=20 m, defined as
$$ \alpha = \frac{z}{U_{horiz}} \frac{d U_{horiz}}{dz}.
$$ AMR-Wind and Nalu-Wind produced nearly identical values for the
TI=0.048, which is close to measured target of 4.5\%, and similar
agreement was found for the shear exponent $\alpha$.  A minor
descrepancy was found in the friction velocity $u_\tau$, with AMR-Wind
resulting in a value slightly lower than Nalu-Wind.

The comparison of the horizontally averaged wind profiles is shown in
figure \ref{fig:CompareAMRvsNaluWind_WSDir}.  At the forcing height
z=20 m, the wind speed and wind shear are close to an exact match
between the two LES codes.  The horizontal wind speeds continue to
agree well for $z$<100 m, beyond which a relatively constant velocity
difference is observed.   For both AMR-Wind and Nalu-Wind, an
approximately linear veer profile was observed until $z\approx$ 250 m,
at which point the wind direction remained constant until the
inversion layer height.

@@

%%%%%%%%%%% Compare Nalu/AMR WS/WDir profiles %%%%%%%%%%%%%%%%%%%%%%%
% Postprocessing/ABLStats/AMRWind_NaluWind_stable_05ms_mesh2_5x2_5x2_5_paper.ipynb
\begin{figure} %[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_WS.png}
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_Wdir.png}\\
  \caption{\label{fig:CompareAMRvsNaluWind_WSDir} Comparison of
    AMR-Wind and Nalu-Wind horizontal velocity and wind direction
    profiles for the stable 5 m/s boundary layer. The dashed
    horizontal line corresponds to the measurement height z=20 m. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% Compare Nalu/AMR TI/Temp profiles %%%%%%%%%%%%%%%%%%%%%%
% Postprocessing/ABLStats/AMRWind_NaluWind_stable_05ms_mesh2_5x2_5x2_5_paper.ipynb
\begin{figure} [hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_TI.png}
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_T.png}
  \caption{\label{fig:CompareAMRvsNaluWind_TTI} Comparison of AMR-Wind
    and Nalu-Wind turbulence intensity and temperature profiles for
    the stable 5 m/s boundary layer. The dashed horizontal line
    corresponds to the measurement height z=20 m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

  \caption{\label{fig:CompareAMRvsNaluSpectra} Comparison of AMR-Wind
    and Nalu-Wind wind spectra at z=20 m for the stable 5 m/s boundary
    layer. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%   \caption{\label{fig:CompareAMRvsNaluRij}
%%     Comparison of AMR-Wind and Nalu-Wind $\langle R_{11}
%%     \rangle$ correlation at z=20 m. }
%% \end{figure}
%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Using the results of the stable cases described in \ref{sec:CFDsetup},
as well as the neutral and unstable ABL computations from the previous study in
Cheung et al. \cite{cheung2020large}, we can examine the influence of wind speed and
stratification on offshore ABL behavior.  In this section we first
compare the differences between the three stable ABL cases, and then
compare their behavior with the previously computed neutral and
unstable counterparts.

\subsubsection{\label{sec:stableABLStats} ABL integrated quantities}
\fxnote{Explain why AMR-Wind only}
From AMR-Wind calculations of the stable ABL at 5 m/s, 10 m/s, and
15 m/s, a number of quantities can be computed to compare with the
measured targets from Archer et al \cite{archer2016predominance}.  In
table \ref{tab:CompareAMRallWS}, we list the TI, shear exponent
$\alpha$, friction velocity $u_\tau$, Obukhov length $L_{Ob}$,
longitudinal lengthscale $L$, and stability classification for each of
these three cases.  The TI values, calculated at the height $z$=20 m
fall within the target range of 4.5\% to 6.0\% for stable conditions
from the Cape Wind measurements.  The calculated friction velocities
are also similar to the values from the neutral offshore ABL
calculations of \cite{cheung2020large}, where $u_\tau$ varied from
0.15 m/s to 0.51 m/s for wind speeds of 5 m/s to 15 m/s.

@@

%%%%%%%%%%%%%%% Compare AMR integrated quantities, all WS %%%%%%%%%%%%%%
% See Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{table}
\caption{\label{tab:CompareAMRallWS} Comparison of Stable ABL for all
  wind speeds} \centering
\begin{tabular}{cccccccc}
  \hline
  Code & Wind speed   & TI     & $\alpha$& $u_\tau$ & Obukhov $L_{Ob}$ & Longitudinal $L$ & Stability \\
  \hline
  AMRWind & 5 m/s      & 0.0483 &  0.166 &  0.157 m/s  &  52.5 m & 27.7 m  & Very stable\\
  AMRWind & 10 m/s     & 0.0506 &  0.160 &  0.319 m/s  &  57.2 m & 29.6 m  & Very stable\\
  AMRWind & 15 m/s     & 0.0550 &  0.118 &  0.511 m/s  & 131.3 m & 43.8 m  & Stable \\
  \hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The qualitative behavior of the stable boundary layers can be seen
through snapshots of the flow taken from each of the simulations.  In
figure \ref{fig:SnapshotsZ20}, instantaneous snapshots of the
horizontal and vertical velocities for each of the three cases at the
z=20 m measurement height are shown.  The largest difference can be
seen in the size of the flow structures between the very unstable and
stable cases.  Longer streaks are evident in the 15 m/s case compared
to the 5 m/s and 15 m/s cases, which is consistent with the nearly
50\% larger integral lengthscale $L$ given in table
\ref{tab:CompareAMRallWS}.  The differences in the vertical velocity
are also evident in figure \ref{fig:SnapshotsZ20}.  At higher wind speeds the
magnitude of the vertical $w'$ fluctuations increase, which plays a
strong role in the growth of the boundary layer.

%%%%%%%%%%% z=20 m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \begin{tikzpicture}
    % 5 m/s plots
    \node[anchor=south west, inner sep=0](image) at (0in,4.50in)
         {\includegraphics[width=3in]{figures/snapshots/05ms/velh_mag_z20.png}};
    \node[align=left] at (1in, 4.50in){(a) horizontal vel, 5 m/s};
    \node[anchor=south west, inner sep=0](image) at (3in,4.35in)
         {\includegraphics[width=3.20in]{figures/snapshots/05ms/velz_z20_samelimits.png}};
    \node[align=left] at (4.25in, 4.50in){(b) vertical vel, 5 m/s};

@@

  \end{tikzpicture}
  \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal
    velocity and vertical velocity, taken at t=20,000 seconds of the
    simulations at height z=20 m, for the AMR-Wind calculation of the
    stable 5 m/s, 10 m/s, and 15 m/s ABL. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Horizontally averaged flow profiles shown in figures
\ref{fig:CompareAMRallWS} and \ref{fig:CompareAMRallTTI} provide a
more quantitative assessment of the ABL evolution.  The rapid growth
of the 15 m/s stable case leads to strong shear throughout the
boundary layer up to the inversion height, while the very stable 5 m/s
and 10 m/s cases showed minimal shear at higher elevations (figure \ref{fig:CompareAMRallWS}).  The
change in wind direction is also indicative of the boundary layer
penetration.  Approximately linear veer profiles are visible up to
heights of $z\approx$250 m and $z\approx$350 m for the 5 m/s and 10
m/s cases, respectively, while the linear veer is present in the 15
m/s stable case up to $z$=650 m.

The behavior of the TI and temperature profiles in figure
\ref{fig:CompareAMRallTTI} closely follows the shear and veer profiles
discussed above.  Despite all cases reaching a similar TI levels at
$z$=20 m, the turbulence decays at different rates for each case until
reaching the top of the boundary layer.  The effect of the different
surface temperature changes is also visible in the horizontally
averaged temperature profiles.  Both the 10 m/s and 15 m/s impose
similar temperature changes (-1.4 K/hr and -1.5 K/hr, respectively)
and similar temperatures at the ocean surface.  However, the
cooling effect in the very stable 10 m/s case is limited to $z$<350
m, similar to the veer and turbulence profiles.

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WS.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WDir.png}
  \caption{ \label{fig:CompareAMRallWS} Comparison of the horizontal
    wind speed and wind direction profile for the stable 5 m/s, 10 m/s,
    and 15 m/s boundary layers. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_TI.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_T.png}
  \caption{ \label{fig:CompareAMRallTTI} Comparison of the turbulence
    intensity and temperature profile for the stable 5 m/s, 10 m/s, and
    15 m/s boundary layers. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
